A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-04-29 paper.tex
Tidied section 2

An abstraction of the game restricts actions available to one of the players.
Specifically, we consider abstractions represented as trees of actions,
referred to as \emph{abstract game trees} (AGTs).  Figure~\ref{fig:agt} shows
an example abstract game tree restricting the environment (abstract game trees
restricting the controller are similar).  In the abstract game, the controller
can freely choose actions whilst the environment is required to pick actions
from the tree.  After reaching a leaf, the enivironment continues playing
unrestricted.  The tree in Figure~\ref{fig:agt} restricts the first and second
environment actions to \texttt{request=1}. It then reaches a leaf of the tree
and continues playing unrestricted.

@@

    \begin{subfigure}[t]{.25\textwidth}

@@

    \begin{subfigure}[t]{.25\textwidth}

@@

@@

@@

    To solve our example, the algorithm begins by invoking a SAT solver to find
    a trace of length $k$ from the initial state to the error state (see
    Figure~\ref{fig:trace}). This trace is used to create an abstract game tree
    by taking the first action in the trace and fixing it as the first action
    in the game tree (Figure~\ref{fig:agt}).  This abstract game tree
    represents the conjecture that \texttt{req=1} may be a good first action.
    Next the solver attempts to find a counterexample to this conjecture by
    finding a trace that avoids the error state with the first environment
    action fixed to \texttt{req=1} (Figure~\ref{fig:trace2}), i.e.  by playing
    the abstract game on behalf of the controller.

@@

The bounded synthesis algorithm solves abstract game trees by invoking a SAT
solver to search for candidate partial strategies. Candidate strategies are
checked by a call to the opponent solver, which also refines the abstract game
tree. The refinements are then solved recursively.  The full procedure is
illustrated in Algorithm~\ref{alg:bounded}.

@@

The tree is first extended to the maximum bound with edges that are labeled
with arbitrary opponent actions (Algorithm~\ref{alg:bounded}, line 14) as shown
in Figure~\ref{fig:extended}.  For each node in the tree, new SAT variables are
introduced corresponding to the state ($X_T$) and action ($U_T$ or $C_T$)
variables of that node. Additional variables for the opponent actions in the
edges of $T$ are introduced ($U_e$ or $C_e$) and set to $\textsc{action}(e)$.
The state and action variables of node $n$ are connected to successor nodes
$\textsc{succ}(n)$ by an encoding of the transition relation and constrained to
the winning condition of the player.

>>>>

An abstraction of the game restricts actions available to one of the players.
Specifically, we consider abstractions represented as trees of actions,
referred to as \emph{abstract game trees} (AGTs).  Figure~\ref{fig:agt} shows
an example abstract game tree restricting the environment (abstract game trees
restricting the controller are similar).  In the abstract game, the controller
can freely choose actions whilst the environment is required to pick actions
from the tree.  After reaching a leaf, the enivironment continues playing
unrestricted.  The tree in Figure~\ref{fig:agt} restricts the first environment
action to \texttt{request=1}. At the leaf of the tree the game continues
unrestricted.

@@

    \begin{subfigure}[t]{.2\textwidth}

@@

    \begin{subfigure}[t]{.3\textwidth}

@@

                            edge from parent [fixed] node [below left=0pt and -5pt] {\texttt{req=2}}

@@

                            edge from parent [fixed] node [above left=-3pt and 0pt] {\texttt{req=2}}

@@

    To solve our example, the algorithm begins by invoking a SAT solver to find
    a trace of length $k$ (here we consider $k=3$) from the initial state to
    the error state (see Figure~\ref{fig:trace}). This trace is used to create
    an abstract game tree by taking the first action in the trace and fixing it
    as the first action in the game tree (Figure~\ref{fig:agt}).  This abstract
    game tree represents the conjecture that \texttt{req=1} may be a good first
    action.  Next the solver attempts to find a counterexample to this
    conjecture by finding a trace that avoids the error state with the first
    environment action fixed to \texttt{req=1} (Figure~\ref{fig:trace2}), i.e.
    by playing the abstract game on behalf of the controller.

@@

The bounded synthesis algorithm solves abstract game trees by invoking a SAT
solver to search for candidate partial strategies. Candidate strategies are
used as game abstractions for the opponent and can be verified by a call to the
opponent solver. The solver recursively refines the abstraction by finding
counterexample strategies. The full procedure is illustrated in
Algorithm~\ref{alg:bounded}.

@@

The tree is first extended to the maximum bound with edges that are labeled
with arbitrary opponent actions (Algorithm~\ref{alg:bounded}, line 14).  For
each node in the tree, new SAT variables are introduced corresponding to the
state ($X_T$) and action ($U_T$ or $C_T$) variables of that node. Additional
variables for the opponent actions in the edges of $T$ are introduced ($U_e$ or
$C_e$) and set to $\textsc{action}(e)$.  The state and action variables of node
$n$ are connected to successor nodes $\textsc{succ}(n)$ by an encoding of the
transition relation and constrained to the winning condition of the player.
